Handling Recursion in Generic Programming Using Closed Type Families

### 2018-04-26 lncs-paper.tex
Polish Sec. 3

Closed type families are the Haskell language extension introduced by Eisenberg et al.~\cite{Eisenberg2014}. The main idea of the extension being that he equations for a \emph{closed type family} are disallowed outside its declaration. Under the extension, we can give the following definition of a type-level equality:
\texttt{
\vs
\indent\textbf{type family} Equal a x \ann Bool \textbf{where}\\
\indent\s\s Equal a a = 'True\\
\indent\s\s Equal a x = 'False
\vs
}
The equations in a closed type family are matched in a top-to-bottom order. Since the order is fixed, the overlapping equations here cannot be used to define unsound type-level equations.

@@

In summary, we claim that any generic function accessing recursive knots in the underlying datatype structure can be defined in the way described above for \texttt{subterms} task. We give another example showing how to adapt our idiom to different scenarios in the following section.

>>>>

Closed type families are the Haskell language extension introduced by Eisenberg et al.~\cite{Eisenberg2014}. The main idea of the extension being that the equations for a \emph{closed type family} are disallowed outside its declaration. Under the extension, we can give the following definition of type-level equality:
\texttt{
\vs
\indent\textbf{type family} Equal a x \ann Bool \textbf{where}\\
\indent\s\s Equal a a = 'True\\
\indent\s\s Equal a x = 'False
\vs
}
The equations in a closed type family are matched in a top-to-bottom order. Since the order is fixed, the overlapping equations here cannot be used to define unsound type-level equations.

@@

In summary, we claim that any generic function accessing recursive knots in the underlying datatype structure can be defined in the way described above for \texttt{subterms} task. We give another example showing how to adapt our idiom to different scenarios in the following subsection.
